---
title: "Advanced R Homework_1"
author: "24204862-Bhargava K"
format: pdf
execute:
  echo: false
  warning: false
  message: false
---

```{r}
library(ggplot2)
```

### ***Introduction:***

The CO2 dataset was utilized in this task. Measurements of plants uptake of carbon dioxide in various environmental are included in this dataset.

```{r}
# Load required dataset
data("CO2")

# Remove rows with missing values for plotting
data <- na.omit(CO2)

# View first few rows of the dataset
head(CO2)
```

The variables include:

-   **Plant:** Plant ID

-   **Type:** Plant origin (Quebec or Mississippi)

-   **Treatment:** Whether the plant was chilled or not

-   **conc:** Ambient CO2 concentration

-   **uptake:** Rate of CO2 absorption (*response variable*)

### *Plotting the dataset*

```{r}
co2_chilled <- subset(data, Treatment == "chilled")

ggplot(co2_chilled, aes(x = conc, y = uptake, color = Type)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(
    title = "CO2 Uptake in Chilled Plants",
    x = "CO2 Concentration", y = "CO2 Uptake",
    color = "Plant Type"
  ) +
  theme_minimal()

```

-   As CO2 concentration goes up, both types of plants absorb more CO2. This is expected because more CO2 in the air generally means more available for photosynthesis.

-   At every concentration level, Quebec plants show higher uptake than Mississippi plants. Their red trend line is steeper and higher, indicating stronger CO2 absorption.

-   Since this plot is only for chilled plants, it suggests that Quebec plants are more efficient at CO2 uptake under cold conditions compared to Mississippi plants.

```{r}
#Creating subset with non-chilled data
co2_nonchilled <- subset(CO2, Treatment == "nonchilled")

# Plotting the non-chilled data.
ggplot(co2_nonchilled, aes(x = conc, y = uptake, color = Type)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(
    title = "CO2 Uptake in Non-Chilled Plants",
    x = "CO2 Concentration",
    y = "CO2 Uptake",
    color = "Plant Type"
  ) +
  theme_minimal()
```

-   As the concentration of CO2 goes up, the uptake rate also increases for both Quebec and Mississippi plants.

-   Compared to the chilled plot, Mississippi plants have higher uptake rates here. That means warmer conditions helped them absorb more CO2.

-   Quebec plants still outperform Mississippi plants across all CO2 levels,their line is higher and steeper.

-   The difference in uptake between the two plant types is smaller under non-chilled conditions, meaning Mississippi plants benefited more from the warmth than Quebec plants did.
